\subsection{Post Database}
Jose I. Retamal
\vskip 0.1in
\indent
\indent
For store post, we need a database that:
\begin{itemize}
	\item Can store a huge amount of data, because posts are the things that occur more in the application because cities and places can have "any" amount of post each we expect that they would more posts that anything in the application. 
	
	\item The post would need to be stored by a city or place, and they would be for one particular city or place. Some sort of indexing would help performance.


\end{itemize}

	In resume, we need a highly scalable database with little structure, on this description fits perfect a document-based database.

We have considered three different document base databases: InterSystems cache, MongoDB, and Apache CouchDB(). We have  chosen MongoDB because:

\begin{itemize}
	\item Simple to use.
	\item It easy to install in the Linux environment.
	\item Native replication is included.
	\item Even if it has fewer features than the others, it is good because we don't really need the extra features.
	\item It has a go driver to access the database. 
\end{itemize}


\subsection{running the services}
Jose I. Retamal
\vskip 0.1in
\indent
\indent
For stor

When it comes to research, the best way to run a service, it looks like there is only one path to follow, the docker container. 

Docker is an open-source project that aims to automate the development, deployment, and running of the applications. Applications run in independent containers that use just the needed amount of resources.

It allows packing the full application for then deployed and run it where needed. 

Advantages of using docker \cite{dockeradv}:

\begin{itemize}

	\item  Fast deployment, no need to set up the environment,we only install docker in the VM, and we are good to go.
	\item  The management of containers is easy. We can manage each service and updated it in a fast way.
	\item  Proper Usage of resources, since the application runs in a container, do not use extra resources.
	\item  Easy and fast start of the containers, the app is running in a few seconds with just one command.
\end{itemize}