\section{Technologie Research and Decision }
Jose I. Retamal
\vskip 0.1in
\indent
\indent
We start with some research about the best technologies that can be used to develop the system. The technologies that we need are:
\begin{itemize}
	\item Backend programming language.
	\item  Communication interface.
	\item  Databases for each service.
	\item  How to store images
	\item  Client technologies.
	\item  How and where run the services.
\end{itemize}



\paragraph{The factors we take into consideration to choose the technologies are:}

\begin{itemize}
	\item Accessibility. Technologies must be accessible without a cost; they can be free and open-source or offer student free usage.
	\item New to us. One of the ideas of the project is to learn how to work with new technologies and learn. So we look for technologies that are not familiar to us.
	
	\item Popular and used in 
	Professionally used. We want to learn how to use technologies that are popular and used in professional software development.
	
	\item Mature and recognized. We prefer technologies with background and maintained/developed by a recognized organization or a big open source community. Even if there are always new technologies coming out, we prefer those that are already established.
	
	\item It adapts well to the purpose need in the system.
	Simple and with resources to learn. We need to learn the technologies, so we instead chose those that are fast to learn and with many resources(tutorials and documentation) to access.
\end{itemize}
